Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-21 paper/example.tex
Add todos and fixed spelling

The AGREE analysis of the cyber-hardened implementation is shown in
\figref{fig:hardened-certificate}. AGREE has generated hihg-level
evidence justifying the claim that the high-assurance components
guarantee the correct behavior of the SW implementation in the
presence of the untrusted AI route planner.  Having passed AGREE
verification, the high-assurance components are ready to be
synthesized.

@@

Preserving the input to output relationship of streams between the
AGREE contracts and CakeML lifts the AGREE contract verification
results to the actual deployed system.  If the contract model
verification succeeds, then the meaning of those results hold for the
deployed system.  These results, however, are only valid under
additional assumptions on the deployed system:
\begin{itemize}
\item contracts for non-synthesized components accurately model their deployed
counterparts;
\item an appropriate schedule exists to sequence component
  execution following the dependent data-flow in the design; and
\item the communication fabric stitching components together works in harmony
  with the schedule.
\end{itemize}

Support and automation for these aspects of the design process are
discussed in other works.\footnote{KLS:need cites to HAMR, seL4, and Adventium work}

>>>>

The AGREE analysis of the cyber-hardened implementation is shown in
\figref{fig:hardened-certificate}. AGREE has generated high-level
evidence justifying the claim that the high-assurance components
guarantee the correct behavior of the SW implementation in the
presence of the untrusted AI route planner.  Having passed AGREE
verification, the high-assurance components are ready to be
synthesized.

@@

Preserving the input to output relationship of streams between the
AGREE contracts and CakeML lifts the AGREE contract verification
results to the actual deployed system.  If the contract model
verification succeeds, then the meaning of those results hold for the
deployed system.  These results, however, are only valid under
additional assumptions on the deployed system:
\begin{itemize}
\item first, contracts for non-synthesized components accurately model their deployed
counterparts;
\item second, an appropriate schedule exists to sequence component
  execution following the dependent data-flow in the design; and
\item third the communication fabric stitching components together works in harmony
  with the schedule.
\end{itemize}
\noindent Support and automation for these aspects of the design process are
discussed in other works.\footnote{KLS:need cites to HAMR, seL4, and Adventium work}

### 2022-03-21 paper/high-assurance-contracts.tex
Add todos and fixed spelling

As previously discussed, transformations carried out in the BriefCASE
interface have created a cyber-hardened system, protecting against
malicious AI behavior, by inserting a high-assurance filter and
monitor between the AI and the WM (see \figref{fig:hardened}). The
filter protects the WM from malformed data and the monitor protects
the WM from (possibly malicious) spontaneous or delayed responses.
These components were added, one at a time, by
\begin{itemize}
  \item selecting the connection in the model where the
    component is to appear,
  \item choosing the appropriate transformation, and
  \item specifying the relevant filtering or monitoring \emph{policy} (behavior).
\end{itemize}

>>>>

As previously discussed, transformations carried out in the BriefCASE
interface have created a cyber-hardened system, protecting against
malicious AI behavior, by inserting a high-assurance filter and
monitor between the AI and the WM (see \figref{fig:hardened}). The
filter protects the WM from malformed data and the monitor protects
the WM from (possibly malicious) spontaneous or delayed responses.
These components were added, one at a time, by
\begin{itemize}
  \item first, selecting the connection in the model where the
    component is to appear,
  \item second, choosing the appropriate transformation, and
  \item third, specifying the relevant filtering or monitoring \emph{policy} (behavior).
\end{itemize}

### 2022-03-21 paper/paper.tex
added definition of evaluation, plus related discussion
Add todos and fixed spelling

\newcommand{\konst}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\imp}{\Rightarrow}
\newcommand{\set}[1]{\ensuremath{\{ {#1} \}}}
\newcommand{\sem}[1]{\ensuremath{[\![ #1 ]\!]}}
\newcommand{\kstar}[1]{\ensuremath{{#1}^{*}}}
\newcommand{\Lang}[1]{\ensuremath{{\mathcal L}({#1})}}
\newcommand{\itelse}[3]{\mbox{$\mathtt{if}\ {#1}\ \mathtt{then}\ {#2}\ \mathtt{else}\ {#3}$}}

@@

\subsection{Revisions}
\begin{compactitem}
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Reformat text to put single sentence on each line.}
  \item Move example to its own repository, archive, and give the DOI and URL for the example.
  \item \sout{Update AGREE certificates with new model}
  \item Separate example into separate files for initial design, cyber-components and tests, hardened design, and seL4 process design.
  \item \sout{Make clear the initial properties for the assumed correct model:}
    \begin{compactitem}
      \item \sout{Assume at the system level that a new automation request is not sent unless the prior request, if any, is acknowledged}
      \item \sout{Assume at all levels input messages are well-formed}
      \item \sout{Guarantee at all levels that waypoint outputs coincide with air vehicle location messages}
      \item \sout{Guarantee that a start from the waypoint manager coincides with an automation response}
      \item \sout{Guarantee for all trusted components that outputs are well-formed}
    \end{compactitem}
  \item Add citations to last paragraph for scheduled AGREE and HAMR.
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Add in the AGREE specification for the system}
  \item \sout{Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)}
\end{compactitem}

>>>>

\newcommand{\konst}[1]{\ensuremath{\mathsf{#1}}}
\newcommand{\imp}{\Rightarrow}
\newcommand{\set}[1]{\ensuremath{\{ {#1} \}}}
\newcommand{\sem}[1]{\ensuremath{[\![ #1 ]\!]}}
\newcommand{\kstar}[1]{\ensuremath{{#1}^{*}}}
\newcommand{\Lang}[1]{\ensuremath{{\mathcal L}({#1})}}
\newcommand{\Eqs}{\ensuremath{\mathit{Eqs}}}
\newcommand{\itelse}[3]{\mbox{$\mathtt{if}\ {#1}\ \mathtt{then}\ {#2}\ \mathtt{else}\ {#3}$}}

@@

\subsection{Revisions}
\begin{compactitem}
  \item Revise the end of the abstract regarding the case studies to be consistent with what ends up in this version of the paper.
  \item Revise the end of the introduction that discusses the case studies to be consistent with what ends up in this version of the paper.
  \item Fix the link to the motivating example to point to the new repository once it is created. Fix in the next section too.
  \item Add discussion on the limitation of the approach: what attacks can and cannot be covered, can valid messages be rejected, etc.
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Reformat text to put single sentence on each line.}
  \item Move example to its own repository, archive, and give the DOI and URL for the example.
  \item \sout{Update AGREE certificates with new model}
  \item Separate example into separate files for initial design, cyber-components and tests, hardened design, and seL4 process design.
  \item \sout{Make clear the initial properties for the assumed correct model:}
    \begin{compactitem}
      \item \sout{Assume at the system level that a new automation request is not sent unless the prior request, if any, is acknowledged}
      \item \sout{Assume at all levels input messages are well-formed}
      \item \sout{Guarantee at all levels that waypoint outputs coincide with air vehicle location messages}
      \item \sout{Guarantee that a start from the waypoint manager coincides with an automation response}
      \item \sout{Guarantee for all trusted components that outputs are well-formed}
    \end{compactitem}
  \item Add citations, and remove KLS footnote to last paragraph---should cite HAMR, seL4, and Adventium.
\end{compactitem}

@@

\subsection{Revisions}
\begin{compactitem}
  \item \sout{Add in the AGREE specification for the system}
  \item \sout{Add in the AGREE verification conditions (e.g., similar to those in the Scheduled Components NFM submission)}
  \item Add reference to the Liskhov principle of safe-substitution when stating that the system contract is a sound abstraction of the implementation.
  \item Add back in a few sentences on the contract for the filter since those have been removed with the addition of the formal definitions.
\end{compactitem}

### 2022-03-21 paper/sw-contract.tex
Add todos and fixed spelling

The guarantees on \linesref{line:sw-guarantee-1}{line:sw-guarantee-3} coincide events and assert well-formed output.
The guarantees on \linesref{line:sw-guarantee-4}{line:sw-guarantee-6} define temporal properties of the component.
\lineref{line:sw-guarantee-4} insists that a start happens with a request or one step after a request.
The guarantee uses the assumption on \lineref{line:sw-assume-3} and does not check for two requests in a row without a start as the assumption precludes that input behavior.
It differentiates with the followed-by operator what is required at time 0, the start must coincide with the request, with what is required after time 0, the start must coincides with the request or is a response to a request one step earlier.
The guarantee also does not force the start to always happen, it only says that if it does happen, it is under the defined conditions.

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
The last guarantee ensures that alert is persistent.
The \texttt{Once} operator is true if the enclosed expression has ever been true before the current moment.
\lineref{line:sw-guarantee-6} ensures if alert has ever happened in the past, then it is happening in the present moment.
These six guarantees define the behavior of the SW component under the three assumptions.

>>>>

The guarantees on \linesref{line:sw-guarantee-1}{line:sw-guarantee-3} coincide events and assert well-formed output.
The guarantees on \linesref{line:sw-guarantee-4}{line:sw-guarantee-6} define temporal properties of the component.
\lineref{line:sw-guarantee-4} insists that a start happens with a request or one step after a request.
The guarantee uses the assumption on \lineref{line:sw-assume-3} and does not check for two requests in a row without a start as the assumption precludes that input behavior.
It differentiates with the followed-by operator what is required at time 0, the start must coincide with the request, with what is required after time 0, the start must coincide with the request or is a response to a request one step earlier.
The guarantee also does not force the start to always happen, it only says that if it does happen, it is under the defined conditions.

\lineref{line:sw-guarantee-5} forces the alert to sound if the start does not arrive within the one-step bound.
Together with \lineref{line:sw-guarantee-4} the contract model allows for non-alerting and alerting behavior.
The last guarantee ensures that alert is persistent.
The \texttt{Once} operator is true if the enclosed expression has ever been true before, or in, the current moment.
\lineref{line:sw-guarantee-6} ensures if alert has ever happened, then it is happening in the present moment.
These six guarantees define the behavior of the SW component under the three assumptions.
